### 2018-02-15 Writing/Thesis/content/abstract.tex
Updated abstract

Although the amount of data available worldwide is increasing, the portion of analyzed data remains low. This problem is caused by a lack of experts in the field that are able to carry out an analysis, and the difficulty of the analysis for non-experts. Especially for the task of classification, there are many algorithms with variing performance values from data set to data set - there does not exist one best algorithm, which one can always recommend. One response to this problem is automated machine learning. Therefore, in this thesis, to approaches to construct a ranking of classification algorithms for a new data set, based on properties of that data set,are presented and compared. The first of the two alternatives works on the basis of regression models; one regression model predicts a performance value for each classifier, from which then a ranking is constructed. In contrast, the second, preference based model directly learns and returns rankings. In the evaluation it became clear that the regression based alternative is superior to the preference based approach; the best evaluated regression model, based on the random forest algorithm, achieved values of up to 0.495 for Kendall's rank correlation coefficient and a peformance loss of 1.308 percent on average. However, the tested preference models are superior at least to the baseline in some scenarios. Therefore the conlucion can be drawn that at least certain properties of data sets are connected to performance values of classification algorithms, which can be exploited by regression and preference models, although the regression approach is superior to the preference alternative within the scope of the conducted evaluation.

>>>>

Although the amount of data available worldwide is increasing, the portion of analyzed data remains low. This problem is likely caused by a lack of experts in the field that are able to carry out an analysis effectively, as it is a difficult task for a layperson. Especially regarding the challenge of classification there exist many algorithms with varying performances from data set to data set - there is no one best algorithm that can always be recommended. One response to this problem is automated machine learning (AutoML): tools that recommend a learning algorithm for a new data set that they estimate to perform best on this particular data set. Current AutoML approaches, however, often search for a fitting algorithm without explicitly taking into account how properties of the data set in question might influence the performances of classifiers. For the most part, they also suggest a single algorithm only. In comparison to the recommendation of a ranking of classifiers this has the disadvantage that no alternatives to the suggested algorithm are presented, which, due to a certain inaccuracy of the prediction, may have an equal or even better performance than the first suggestion regarding the examined data set. The problem considered in this thesis is thus the construction of a ranking of classification algorithms in relation to properties of a data set. Two different approaches that aim to solve this problem are presented and compared. The first alternative works on the basis of regression models: one regression model for each classifier predicts a performance value for that classifier. On the basis of the predicted performance values, a ranking then is constructed. In contrast, for the second approach, a preference-based model directly learns and returns rankings. In the evaluation of the two alternatives, it became apparent that the regression-based alternative is superior to the preference-based approach. However, the tested preference models also achieved a significant advantage compared to the static baseline used in the evaluation, at least in certain scenarios.
